Stochastic Variance Reduced Policy Gradient

### 2018-02-02 svrpg.tex
correzioni

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
We use two different adam hyperparameters: one for updates tied to snapshot points and the other tied to the updates of sub-iterations points.
\todomat{$\uparrow$ explain better: it's not only two separate meta-parameters, but two separate learning rate schedules. Use notation from previous sections, \eg snaphot is usually associated with $\tilde{\vtheta}$} 
This is because we are dealing with two different variance magnitudes.
\todomat{$\uparrow$ the reason is this, but try to spend more words on it}
Denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and denote by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.

>>>>

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
\todomat{$\uparrow$ the opening of the section could connect better with previous sections. Declare which meta-parameters will be addressed in the section}
A common way to reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2014adam}, a method that computes adaptive learning rates for each parameter. Adam helps to stabilize the gradient estimate by computing adaptive learning rates for each parameter based on the history of the gradients' variance.
Due to this feature we can use two different adam in order to properly leverage the structure of the proposed SVRPG update. The first adam will be associated to the snapshot updates and the second one will be associated to the sub-iteration updates. By doing so we are decoupling the contribution to the variance introduced by the snapshots from that one introduced by the sub-iterations, which lie, respectively, on two different order of magnitude.Therefore, we are able to properly adapt the learning rate in each situation. 
\todomat{$\uparrow$ explain better: it's not only two separate meta-parameters, but two separate learning rate schedules. Use notation from previous sections, \eg snaphot is usually associated with $\tilde{\vtheta}$} 
This is because we are dealing with two different variance magnitudes.
\todomat{$\uparrow$ the reason is this, but try to spend more words on it}
Denote by $\alpha_{snap}$ the learning rate associated to the last snapshot and denote by  $\alpha_{sub-iter}$ the learning rate associated to the current sub-iteration.
